The language of generalization: Probability, vagueness, and interaction

### 2018-04-24 paper/comgen-paper.Rmd
final edits throughout discussion, add alternative haslanger analysis, update bib

<!-- a useful representation  -->
<!-- How do we come to know things?  -->
<!-- How does one acquire inductive beliefs? -->
Probability is a useful representation for human generalization from observations [@Shepard1987].
If you observe several *wugs* (a novel category) that have two legs, you might infer that all wugs have two legs.
But not all properties have such strong projectibility.
Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2008].
Bayes Rule provides the way to update one's prior beliefs with some obesrvational data $d$: $P(p \mid d) \propto P(d \mid p) \cdot P(p)$, assuming some generative process that resulted in the observed data---summarized in the likelihood $P(d \mid p)$ [@Tenenbaum2001].

@@

The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to eachother succinctly in language.
Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Staring at the sun makes you go blind.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalized in terms of predictive probability.
Critically, deploying this simple semantics within a formal framework for pragmatic language understanding leads to complex interactions with background knowledge.
<!--
formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types, illustrated here with categories, events, and causes.

Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
-->
We tested this theory by exploring its implications for truth judgments, operationalized as a speaker's decision about whether it would be useful to utter the generalization. 
Endorsement, we have shown, depends in systematic ways on the listener's prior beliefs about prevalence.
This framework accounts for a number of philosophically puzzling generic statements (Expt. 1), naturally extends to other domains of generalizations (habituals and causals; Expts. 2 \& 3), and provides an avenue for top-down moderators on language use by way of predictive probability (Expt. 2c).
We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
In each case our model provided strong quantitative fit to human judgements.

@@

\mht{let me know where, if anywhere, we should mention "double generalizations" (e.g., generics about habitual properties)}

\ndg{
[these paragraphs were out of place here. perhaps incorporate later...]
By precisely articulating the conditions under which generalizations are true or false, we are able to describe how an agent should update its beliefs based on that sentence. 
Thus, in addition to providing a quantitative understanding of the phenomena of the language of generalization, formalizing this language opens up the possibility of building models that learn abstract, generalizable knowledge from language.
xx
We note that regressions model that take into account the referent prevalence and the distinctiveness of the feature (e.g., cue validity) do reasonable jobs at explaining some of the variance in the endorsement data.
These kinds of model, however, do not represent bonafide theories of the semantics of generalizations; they are merely a re-description of the data.
<!-- \ndg{this point is unclear. maybe save it for general discussion?} -->
A theory of the semantics of a generalization must formalize the conditions under which the generalization is true or false as well as how those truth-conditions relate to endorsement. 
That is precisely what our information-theoretic model does.
xx
The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from world knowledge.
This formal separation is a key advancement beyond previous theoretical accounts, which have either aimed to account for context-sensitivity by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
That is, we provide a route for precise quantitative influence of world knowledge on generic language by way of shared background knowledge between speakers and listeners, which at its base takes the form of a prevalence prior.
Our communicative framework also includes a model of a listener who interprets generalization.
Such a quantitative model makes further predictions about domain-general learning from the language of generalization, which we leave for future work. 
}
<!-- Our model formalizes a simple meaning for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data. -->

@@

This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
These predictive probabilities are fundementally mental representations and not observable frequencies, the object of other statistical approaches to genericity.
Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003] or merely correlational happenstance.
What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.

@@

Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding the numerical language used to convey explicit probabilities, a historically quite recent innovation [cf., @Levinson1995]. 
Rather than conveying probabilities *explicitly*, generalizations convey them *implicitly*.
In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].

@@

Conceptual structure, including higher-order abstractions, can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
We believe such probabilistic concept representations can be adopted as a formal analog to intuitive theories of natural kinds [@Gelman2003; @Keil1992].
We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model. 
The important commonality among different domain-specific background theories is that they each have a statistical layer to them (i.e., they each support prediction via beliefs about *prevalence*), which language interfaces with via the tools of truth-functional semantics.
Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.

The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is peripheral to communicating with generalizations.
Our model distinguishes the semantic contribution of an utterance from a speaker's utility in producing that utterance. 
For simplicity, the mode presented here assumes these two are the same: they are both about prevalence. 
However, the model makes nearly identical predictions if the speaker's utility comes from communicating the abstract parameters of the prevalence distributions (i.e., if the communicative goal is less about prevalence and more about the kind of thing that the referent is).
This behavior is promising for constructing models of generalizations that teach about the abstract relations present in intuitive theories of kinds and properties.

@@

The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity of the language of generalizations highlighted in this paper.
An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall").
Recent empirical and computational modeling work suggests that pragmatic reasoning combined with world knowledge can flexibly adjust the comparison class to appropriately suit the context [@Tessler2017].
In this paper, we do not include such a mechanism in our model, instead we made the comparison class clear to participants when possible in order to study the remaning context-sensitivity with generics.
<!-- \ndg{say something about how the comparison class might be set, cite your cogsci paper, say why this paper is ok without this: we made comparison class clear to Pp in order to study remaining issues with generics.} -->

@@

Finally, the comparison classes used in our case studies were with always respect to the category (*other animals*, *other people*, *other possible causes*).
Thus, our endorsement model assumes the goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud], was to address the question of "*what* has feature?".
Were the QUD to be reversed (e.g., "what features does the category have?"), the comparison classes would be constructed with respect to the feature (e.g., *other features*, *other actions*, *other effects*).
It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
The statement "Lawyers care about the law." can be interpreted with a category-wise comparison class (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law."; imagine a pedagogical context) or a feature-wise comparison class (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*" e.g., when said sardonically).
Prosodic focus easily gates between these interpretations (e.g., "[Lawyers] care about the law" vs. "Lawyers care about [the law]").
\ndg{mention that prosodic focus easily switches between these.}
In this work, we focused on category-wise comparison classes purely for methodological convenience.
Future work should investigate the factors that give rise to feature-wise interpretations of generalizations and how the relevant comparison classes are constructed.

@@

Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common it is in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
<!-- from a formal perspective is that generic language is far from trivial to characterize.  -->
<!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
Generalizations are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is, in fact, easier to formalize but more difficult for young children to acquire [@Brandone2014; @Gelman2015].
<!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
<!-- The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development. -->
<!-- In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a]. -->
This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) are inappropriate for generalizations [@Leslie2008].

Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) = \{p :p > \theta\}$ requires learning at least three distinct aspects of meaning: 
(1) the *dimension* being described (i.e., probability $p$),
(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
(3) the value of the *threshold* (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
Upon repeated cross-situational data with quantifiers, this prior could be updated towards acquiring a fixed meaning.
However, for generalizations, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
Thus, under our framework, generalizations should not only be learned before quantifiers but also faciliate the acquisition of quantifiers.
<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
<!-- This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data. -->

There is a secondary argument for why our semantics presents an easy learning problem.
<!-- The uniform prior over the threshold $\theta$ in the truth-functional semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy. -->
Uniform uncertainty over values in the unit interval $[0, 1]$ for threshold $\theta$ in a threshold-function (as we have assumed in our model) is mathematically equivalent to a *soft semantics* wherein the degree to which the utterance is true is proportional to the degree itself, in this case prevalence $p$: $\int_{0}^{1} \delta_{p > \theta} \diff \theta = p$
This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.
The difficulty in acquiring the meaning of quantifiers, then, is a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
We leave for future work the precise implementation of the acquisition model we sketch out here.

@@

The present paper presents the first formal theory of genericity in language that makes accurate and precise quantitative predictions about human behavioral data. 
A number of other theories of genericity have been proposed in the formal semantics  literature.
<!-- We now turn to situating our account with respect to these previous theories. -->
<!-- By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*. -->
These theories fall into two broad camps: Those that appeal to the statistics of the world (e.g., how many Ks have F) and those that appeal to conceptual representations (e.g., *there is something about being K which causes it to F*).
Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]

@@

\mht{from above:
Beliefs about prevalence will often be the result of conceptual knowledge about kinds and properties [@Leslie2007; @Leslie2008; @Prasada2013].
Such knowledge is not necessary, however: Relevant background knowledge may be merely correlational in nature.
The prevalence prior is a common representation that provides the glue between conceptual and statistical knowledge and natural language semantics.
The truth conditions of generalizations depend only on prevalence, but prevalence depends upon knowledge.
}

The relation of our account to the conceptual accounts of @Leslie2008 and @Prasada2012 has been described above.
\ndg{actually, i think it's better to have a specific section for these conceptual theories here. can leave a but of high-level discussion of prevalence priors in relation to bayesian intuitive theories above, and then talk about details of leslie and prasada here...}
We reiterate that the key point of divergence between the conceptual accounts and our view concerns the core, semantic meaning of the language of generalization.
Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
For us, the semantics concerns a probability, which is the byproduct of a conceptual structure, but it is not the conceptual structure itself. 
We believe this separation provides a more unifying view of the phenomena of generics, giving a single metric as the basic currency for the language of generalizations: the metric of probability.

In addition, our model provides a path towards unifying conceptual and statistical approaches to generics. 
Our semantic representation is inherently statistical: Natural language semantics only gets to operate on prevalence. 
At the same time, utterances are interpreted by listeners whose beliefs about prevalence result from internal models of how the world works.

>>>>

<!-- a useful representation  -->
<!-- How do we come to know things?  -->
<!-- How does one acquire inductive beliefs? -->
Probability is a useful representation for human generalization from observations [@Shepard1987].
If you observe several *wugs* (a novel category) that have two legs, you might infer that all wugs have two legs.
But not all properties have such strong projectibility.
Seeing a wug with broken wings tells you comparatively less about other wugs having broken wings [@Nisbett1983].
Abstract, potentially domain-specific, beliefs about the projectibility of different properties can be represented by a probability distribution over the prevalence $P(p)$ [@Kemp2007].
Bayes Rule provides the way to update one's prior beliefs with some obesrvational data $d$: $P(p \mid d) \propto P(d \mid p) \cdot P(p)$, assuming some generative process that resulted in the observed data---summarized in the likelihood $P(d \mid p)$ [@Tenenbaum2001].

@@

The human species is remarkable not only because we can extract useful generalizations from observations of the world, but because we can convey these generalizations to each other succinctly in language.
Generalizations expressed in language (e.g., "John runs.", "Dogs are friendly.", "Fire causes smoke.") are a premier example of how simple statements---statements understood by even the youngest language users---can convey subtle meanings and display complex sensitivities to context.
We have argued that the core meaning of such linguistic expressions can be understood by a vague threshold function that operates over a speaker's inductive beliefs, formalized in terms of predictive probability.
Critically, deploying this simple semantics within a formal framework for pragmatic language understanding leads to complex interactions with background knowledge.
<!--
formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
As a formal theory of the language of generalization, our framework unifies large swaths of language about distinct semantic types, illustrated here with categories, events, and causes.

Generalization underlies each of these, and we formalize their meaning by appealing to prevalence, which we define as a predictive probability (as opposed to frequency).
-->
We tested this theory by exploring its implications for truth judgments, operationalized as a speaker's decision about whether it would be useful to utter the generalization. 
Endorsement, we have shown, depends in systematic ways on the listener's prior beliefs about prevalence.
This framework accounts for a number of philosophically puzzling generic statements (Expt. 1), naturally extends to other domains of generalizations (habituals and causals; Expts. 2 \& 3), and provides an avenue for top-down moderators on language use by way of predictive probability (Expt. 2c).
We have provided strict tests of our formal model by both measuring and manipulating listeners' background knowledge as well as comparing our model to a number of alternatives.
In each case, our model provided strong quantitative fit to human judgements while other models fall short.

Ours is a psychological model that leverages the insights of truth-functional semantics to articulate how an agent should update their beliefs based on a generic sentence. 
The Bayesian model provides a clean separation of the semantics of a generalization (represented formally by a threshold-function) from world knowledge (represented by the prevalence prior).
Previous theoretical accounts have either aimed to account for the context-sensitivity of generics by positing distinct semantic constructs [e.g., *relative* vs *absolute* generics, described below; @Cohen1999] or positing a semantics that cannot be separated from world knowledge [@Leslie2008].
Here, we demonstrate how the context-sensitivity of generics can emerges via the interplay of a stable (but vague) semantics and diverse background knowledge.

\mht{unsure about this paragraph... a version of it may be better for the cover letter (if at all)}
<!-- Not all theories are created equal, however.  -->
Even the most influential of extant theories generally makes one or a few predictions about "different kinds" of generics, and leave it to intuition to decide for a particular generic statement, what kind of generic it is.
In this paper alone, our theory has made hundreds of predictions about the endorsement of individual generic statements, with high accuracy, derived from a general theory that we posit applies to all generic statements.
In addition, previous accounts are rarely general enough to include generalizations of different semantic types (e.g., *habituals*) and deal only with generics.
For these reasons alone, our account is novel.

@@

<!-- Thus, in addition to expressing a precise hypothesis about the truth conditions of generics, instantiating it in a cognitive model opens up the possibility of building more elaborate models that learn abstract, generalizable knowledge from language. -->

<!-- We note that regressions model that take into account the referent prevalence and the distinctiveness of the feature (e.g., cue validity) do reasonable jobs at explaining some of the variance in the endorsement data. -->
<!-- These kinds of model, however, do not represent bonafide theories of the semantics of generalizations; they are merely a re-description of the data. -->
<!-- <!-- \ndg{this point is unclear. maybe save it for general discussion?} --> -->
<!-- A theory of the semantics of a generalization must formalize the conditions under which the generalization is true or false as well as how those truth-conditions relate to endorsement.  -->
<!-- That is precisely what our information-theoretic model does. -->
<!-- xx -->
<!-- The formal Bayesian model we articulate provides a clean separation of the semantics of a generalization from world knowledge. -->

<!-- That is, we provide a route for precise quantitative influence of world knowledge on generic language by way of shared background knowledge between speakers and listeners, which at its base takes the form of a prevalence prior. -->
<!-- Our communicative framework also includes a model of a listener who interprets generalization. -->
<!-- Such a quantitative model makes further predictions about domain-general learning from the language of generalization, which we leave for future work.  -->

<!-- \mht{let me know where, if anywhere, we should mention "double generalizations" (e.g., generics about habitual properties)} -->

<!-- \ndg{ -->
<!-- [these paragraphs were out of place here. perhaps incorporate later...] -->
<!-- } -->
<!-- Our model formalizes a simple meaning for generalizations and investigates the structure of world knowledge that could give rise to the context-sensitivities observed in the data. -->

@@

This paper puts forth the theory that the language of generalization communicates predictive probabilities from speaker to hearer.
These predictive probabilities are not observable frequencies, the object of other statistical approaches to generics, but mental representations.
Probabilities encode predictions about the future and are subject to top-down moderation (e.g., by way of intuitive theories).
Predictions about the presence of a feature can be the result of beliefs about internal causes of the feature [e.g., in an essentialist view of natural kinds; @Gelman2003], generative kind representations [@Prasada2009], or merely correlational happenstance.
What matters for their influence on generic endorsement, however, is their influence on subjective, predictive probability or *prevalence*.

@@

Communicating probabilities might seem contrary to the long attested failures in reasoning about probability [@Tversky1974].
Our theory suggests that the problems with understanding probabilities observed in classic, cognitive psychology paradigms are a problem in understanding explicit probabilities expressed using *numerical language*, a historically quite recent innovation [cf., @Levinson1995]. 
Rather than conveying probabilities explicitly, generalizations convey them implicitly.
In other words, we argue that the utterance "70% of birds fly" is a precise statement about how many birds fly in the way that "John is 6'3"" is a precise statement about the height of John, whereas "Birds fly" is a vague statement more akin to utterance "John is tall".
The latter statements are easier to process, understood at an earlier age, and may be more useful for human reasoning. 
Indeed, young children are actually quite good with reasoning about probabilities, but in ways that are not explicit or tied to the numerical language of probability [@Xu2008; @xu2009statistical].

@@

Conceptual structure, including higher-order abstractions, can be formalized in probabilistic causal models [@pearl1988probabilistic; @Gopnik2003theory] and their generalization in probabilistic programs [@Goodmanconcepts].
We believe such probabilistic concept representations can be adopted as a formal analog to intuitive theories of natural kinds [@Gelman2003; @Keil1992].
We do not assume a particular view of natural kinds in our model, but note that viewing natural kinds as richly structured categories with clusters of non-obvious properties is compatible with our information-theoretic communicative model. 
The important commonality among different domain-specific background theories is that they each have a statistical layer to them (i.e., they each support prediction via beliefs about prevalence), which language interfaces with via the tools of truth-functional semantics.
Thus, our theory provides a separation between conceptual knowledge and the semantics of generalizations; the interface between the two is predictive probability or *prevalence*.

The fact that conceptual knowledge is not a part of our formal semantics does not imply that such knowledge is peripheral to communicating with generalizations.
Not only does conceptual knowledge influence interpretation via prevalence priors, but it may very well be what the speaker intends to communicate.
Like other probabilistic pragmatic models, our model distinguishes the semantic contribution of an utterance (what enters into the truth-functional semantics) from a speaker's utility in producing that utterance. 
For simplicity, the model presented here assumes these two are the same: the speaker's utility comes from conveying prevalence. 
However, the model makes nearly identical predictions if the speaker's utility comes from communicating the abstract parameters of the prevalence distributions [e.g., if the speaker intends to convey that "K is the kind of thing that Fs"; cf., @Prasada2006].
This result is promising for constructing models of speakers with the goal of teaching about the abstract relations between kinds and properties.

@@

The existence of comparison classes is uncontroversial in the study of *vague* or *underspecified* language [e.g., gradable adjectives like *tall* and vague quantifiers like *many*; @Bale2011; @Solt2009].
Adult judgments of the felicity of gradable adjectives like *tall* or *dark* depend upon fine-grained details of the statistics of the comparison class [@Qing2014; @Schmidt2009; @Solt2012] in ways directly analogous to the context-sensitivity of the language of generalizations highlighted in this paper.
An important problem for comparison classes for both gradable adjectives and generalizations is that the comparison class often goes unsaid (e.g., "John is tall for a person" is often produced as just "John is tall"; "Robins lay eggs relative to other animals" is just "Robins lay eggs").
Recent empirical and computational modeling work suggests that pragmatic reasoning combined with world knowledge can flexibly adjust the comparison class to appropriately suit the utterance in context [@Tessler2017].
In this paper, we do not include such a mechanism in our model; instead, when possible, we make the comparison class clear to participants in order to study the remaning context-sensitivity with generics.
<!-- \ndg{say something about how the comparison class might be set, cite your cogsci paper, say why this paper is ok without this: we made comparison class clear to Pp in order to study remaining issues with generics.} -->

@@

Finally, the comparison classes used in our case studies were constructed with respect to the category (*other animals*, *other people*, *other possible causes*).
Thus, our endorsement model assumes the goal of communication, sometimes referred to as the *Question Under Discussion* or QUD [@roberts1996qud], was to address the question of "*what* has feature?".
Were the QUD to be reversed (e.g., "what features does the category have?"), the comparison classes would be constructed with respect to the feature (e.g., *other features*, *other actions*, *other effects*).
It has long been noted that the same generalization can be used to address multiple QUDs [@KrifkaGenericBookFocus], and we posit that differences in interpretation are the result of multiple distinct comparison classes competing for influence.
Prosodic focus can gate between different interpretations: "*Lawyers* care about the law." suggests a category-wise comparison class perhaps in a pedagogical context (i.e., "Lawyers *(as opposed to doctors, firefighters, ...)* care about the law.") while "Lawyers care about *the law*" suggests a feature-wise comparison class perhaps produced by a sardonic speaker (i.e., "Lawyers care about the law *(as opposed to justice, doing what is morally right, ...)*").
Pragmatic reasoning is likely useful as well [cf., @Declerck1986; @Tessler2017].
In this work, we focused on category-wise comparison classes purely for methodological convenience.
Future work should investigate the factors that give rise to feature-wise interpretations of generalizations and how the relevant comparison classes are constructed.

@@

Perhaps the most surprising aspect of the language of generalization is how difficult it is to formalize, given how common it is in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004].
<!-- from a formal perspective is that generic language is far from trivial to characterize.  -->
<!-- Generalizations are common in child-directed and child-produced speech [@Gelman1998; @GelmanEtAl2004] and are believed to be central to the growth of conceptual knowledge [@Gelman2004], -->
Generics are often contrasted with quantifier language (e.g., "some", "most", "all", ...), which is, more difficult for young children to acquire [@Brandone2014; @Gelman2015], but easier to formalize.
<!-- If generics convey something about the probabilty of a feature, we would expect them to be in some way comparable to quantifier statments (e.g., "some", "most", "all", ...). -->
<!-- The extreme flexibility of generic meaning (e.g., "Birds lay eggs" vs. "Birds are female") stands in stark contrast to its early emergence in development. -->
<!-- In fact, quantified statements, whose formal meaning is much more straight-forward (e.g., "Some" means more than zero), emerge *later* in development [@Brandone2014; @Gelman2015], and are often confused for generic statements [@Leslie2012a]. -->
This asymmetry between the simplicity of the formal theory and the age of acquisition has led some to conclude that the normal tools for describing the semantics of quantified utterances (i.e., a truth-functional threshold) are inappropriate for generics [@Leslie2008].

Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
With some reasonable assumptions about the hypothesis space of semantic meanings, the acquisition of a threshold-based truth-functional meaning $\denote{u}(p, \theta) = \{p :p > \theta\}$ requires learning three distinct aspects of meaning: 
(1) the *dimension* being described (i.e., prevalence $p$),
(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
(3) the value of the *threshold* (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
Upon repeated cross-situational data with quantifiers, this prior could be updated towards acquiring a fixed meaning.
However, for generics, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
Thus, under our framework, generics should not only be learned before quantifiers but also faciliate the acquisition of quantifiers.
<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
<!-- This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data. -->

There is a secondary argument for why our semantics presents an easy learning problem.
<!-- The uniform prior over the threshold $\theta$ in the truth-functional semantics (as we have assumed in our model) provides a secondary argument for why acquiring our semantics for generics should be easy. -->
We have assumed the truth functional threshold $\theta$ comes from a uniform distribution over the unit interval $[0, 1]$, which is mathematically equivalent to a *continuously-valued* or *soft semantics* wherein the degree to which the utterance is true is proportional to the degree itself, in this case prevalence $p$: $\int_{0}^{1} \delta_{p > \theta} \diff \theta = p$.
The model for generic interpretation (Eq. \ref{eq:L0}) then becomes: $Lit(p \mid u) \propto p \cdot P(p)$
This *soft semantics* (corresponding intuitively to a meaning like "the higher the probability, the better", or simply "more is better") is perhaps the simplest quantitative semantics one could posit.
The difficulty in acquiring the meaning of quantifiers, then, is a difficulty in recognizing a fixed-threshold semantics as a special case of this *more is better* semantics.
We leave for future work the precise implementation of the acquisition model sketched out here.

@@

The present paper presents the first formal theory of genericity in language that generates quantitative predictions about human behavioral data. 
A number of other theories of genericity have been proposed in formal semantics and in psychology, which posit different constructs or psychological mechanisms to account for the context-sensitivity of generics.
These accounts fall into two broad camps: Those that appeal to quantification or the statistics of the world (e.g., how many Ks have F) and those that appeal to conceptual representations or abstract beliefs (e.g., *there is something about being K which causes it to F*).
Statistical and conceptual theories express the major contrasting views of the truth conditions of generic statements [@Carlson1995essay].^[We use the terms statistical and conceptual to refer to what @Carlson1995essay referred to as "inductive" and "rules and regulations" views, respectively.]

In our account, the core meaning of generics concerns probability (the currency of belief), which in many cases may be the byproduct of rich conceptual structure. 
The separation between conceptual structure (which exists in the head) and prevalence (a quantitative metric for natural language semantics) provides a unified view of the phenomena of generics and a single answer to the semantic question: "what do generics mean?"
By formalizing how background knowledge influences generic understanding, our model provides a path towards unifying conceptual approaches to generics with an inherently statistical natural language semantics.
<!-- At the same time, utterances are interpreted by listeners whose beliefs about prevalence result from internal models of how the world works.  -->

<!-- By contrast, our theory has made hundreds of predictions about individual generic statements, derived from a general theory that we posit applies to all generic statements. -->
<!-- We now turn to situating our account with respect to these previous theories. -->
<!-- By and large, these theories are concerned with explaining *generics* or generalizations about categories, so in keeping with the spirit of these authors, we will refer to the object of explanation, without loss of generality, as *generics*. -->

@@

Conceptual accounts try to identify the core meaning of a generalization directly with aspects of conceptual structure.
The most influential account in psychology comes from @Leslie2008. 
Leslie uses the same starting point as our account: Generics express generalization. 
She then turns her attention to the psychological literature on infant generalization to argue that generics tap into an innate, default mechanism that signals the child (or adult) to generalize the property to the kind.^[
  Because the mechanism for understanding generics is innate, in her account, the learning puzzle (vis a vis quantifiers) immediately goes away.
]
Leslie describes the *default generalization* mechanism as having three components: the ability to (i) identify whether or not F is a *characteristic* property of K (e.g., one characteristic property for an animal would pertain to the mode of locomotion for the animal), (ii) identify whether or not F is *striking* (e.g., can kill you; "Mosquitos carry the West Nile Virus"), and (iii) segment *counterinstances* (Ks which do not have F) into positive and negative counterinstances (i.e., Ks which have some alternative positive property *alt F* and Ks which simply lack F, respectively).^[
  This positive vs. negative counterinstance distinction is a rather technical consideration [though not without psychological foundation, see @Leslie2008, p.36] used to account for the difference between examples like "Birds lay eggs" vs. "Birds are female". 
  For the latter, male birds are positive counterinstances because they have an alternative property (being male). 
  For the former, male birds are negative counterinstances because they simply lack the property (i.e., male birds do not reproduce by some other method).
  We will not discuss this consideration any further other than to note that that the difference between "Birds lay eggs" and "Birds are female" can be explained by by a different mechanism (e.g., informativity with respect to a prevalence prior).
  The notion that alternative features may come into play in generic interpretation may also be addressed with feature-wise comparison classes (described above).
]
On this account, generics are true if *some* Ks have F when all counterinstances are negative and the property is either characteristic or striking. 
If the property is neither characteristic or striking, then almost all Ks must have F for the generic to be true (e.g., "Barns are red").

#### Striking generics

The evolutionary argument for accepting striking generics (e.g., "Tigers eat people") is straightforward: These are relevant properties to know about if you want to survive. 
But there are two other factors that are confounded with striking properties that make it difficult to evaluate a claim about strikingness *per se* (as opposed to beliefs about prevalence) leading to generic endorsement.
The first is that striking properties are rare in the environment: Most animals do not maul children, eat swimmers, or carry malaria.
Thus, the prevalence prior distributions of these features may be hard to distinguish from properties that are just generally rare and distinctive (e.g., *having extraordinarily beautiful feathers*; see also our Expt. 2a, e.g., the distributions for *steals cars* vs. *climbs mountains* for an example with habituals). 
@Cimpian2010 (Expt. 4) found participants willing to endorse generics about both striking properties (e.g., "Lorches have dangerous feathers") and distinctive properties (e.g., "Lorches have distinctive feathers") about equally as often each other and more so than neutral properties (e.g., "Lorches have purple feathers"). 
This similar increase in endorsement for striking and distinctive properties suggests that the prevalence prior $P(p)$ distributions for the two are similar.
@Cimpian2010's experiments did not measure the prevalence prior distribution, but we have found in pilot work that the prevalence prior distribution changes to resemble that of a distinctive property when participants are supplied information about the dangerousness of a property.

The second factor confounded with striking properties is that striking properties may be projected more strongly (i.e., generalized to more instances of the category) than neutral properties.^[
  This observation is also made by @Leslie2008 (p.42), who uses it as motivation for elevating striking properties to their special status in her theory.
]
Interesting, this enhanced projectibility holds for both dangerous properties (e.g., people doing criminal actions) as well as neutral but distinctive properties [e.g., people taller than 6'5"; @Rothbart1978, Expts. 2 & 3].
Thus, there is evidence for the influence of strikingness on *predictive prevalence*, which we posit is an intermediate representation between conceptual knowledge and generic endorsements.
Thus, strikingness may influence endorsement by either (i) altering the prevalence priors or (ii) influencing speaker's predictions about future prevalence; we do not know of any evidence that shows an effect of strikingness while controlling for these mediating factors.

#### Principled and statistical connections

@Leslie2008's notion of *characteristic* properties is similar to @Prasada2006's notion of a *k-property* (*k* for kind), which is a property that bears a *principled connection* to the kind. 
A property bears a principled connection to the kind if a generic sentence of the following form is endorsed:
"Ks, by virtue of being the kind of things that they are, F" (e.g., "Dogs, by virtue of being the kind of things that they are, are four-legged"); if such a sentence is not endorsed (e.g., "Barns, by virtue of being the kind of things that they are, are red") while the simple bare plural is endorsed (e.g., "Barns are red"), then the property is thought to bear a *statistical connection* to the kind (a so-called *t-property*, for emphasizing that it is the *tokens* having the property which matters for generic endorsement).
@Prasada2013 showed that different kinds of generic statements (e.g., characteristic properties with low prevalence, striking properties, etc., see our Expt. 1) support different kinds of inferences (e.g., *by virtue of*, *normative*: "Dogs are supposed to have four legs", *aspect*: "Having four legs is one aspect of being a dog").
Additionally, there is some evidence that the impact of principled connections on interpretations is separate from their influence on beliefs about prevalence [@Prasada2006].
